---
title: "MPG Analytics"
author: "Kiefer Maddex"
date: '2022-05-04'
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(dplyr)
```

## MPG Analysis
Using a online dashboard will eliminate the need for distributing files and reduces the potential of errors in replication. This app is a proof of concept for a simple scenario exemplifying the relationship between car weight, number of cylinders and MPG. All inputs can be adjusted and changed. All output are fully reactive.


## MPG Analysis
- Adjustable Inputs:
  - Input 1 = Engine displacement (default 300)
  - Input 2 = Number of cylinders (default 6)
  
- Checkbox: 
  - Linear regression model (show/hide)
  
- Results: 
  - Linear regression trend analysis of weight to MPG identifying number of cylinders


## MPG Analysis - R Code

```{r cars, echo = TRUE, eval = FALSE}
library(dplyr)

carmodel <- filter(mtcars, mtcars$disp <= input$slider1$, 
                   mtcars$cyl <= input$slider2)

plot(carmodel$mpg, carmodel$disp, ylab = "Engine Disp", 
     xlab = "MPG", pch = 16, col = carmodel$cyl)

model1 <- lm(disp ~ mpg, data = carmodel)
abline(model1, col = "blue", lwd = 2, lty = 3)

legend(30, 165, c("8 Cylinders", "6 Cylinders", "4 Cylinders"), 
       pch = 16, col = c("grey", "darkmagenta", "dodgerblue"), 
       bty = "n", cex = 1 )
```

## MPG Analysis - Graph

```{r output}
carmodel <- filter(mtcars, mtcars$disp <= 300, mtcars$cyl <= 6)

plot(carmodel$mpg, carmodel$disp, ylab = "Engine Disp", xlab = "MPG", pch = 16, col = carmodel$cyl)

model1 <- lm(disp ~ mpg, data = carmodel)
abline(model1, col = "blue", lwd = 2, lty = 3)

legend(30, 165, c("8 Cylinders", "6 Cylinders", "4 Cylinders"), pch = 16,
           col = c("grey", "darkmagenta", "dodgerblue"), bty = "n", cex = 1 )
```

